---
title: "Sum score analysis for Market Profile crime indices"
author: "Ivan L. Simpson-Kent (coding) and Martins M. Gatavins (curation)"
date: "2023-07-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# R version 4.2.3
# RStudio
library(readr) # v 2.1.4
library(dplyr) # v 1.1.1
library(stringi) # v 1.7.12
library(stringr) # v 1.5.0
library(tidyr) # 1.3.0
library(corrplot) # v 0.92
library(qgraph) # v 1.9.4
library(psychonetrics) # v 0.10
library(networktools) # v 1.5.0
library(Matrix) # v 1.5.3
library(OpenMx) # v 2.21.1
library(bootnet) # v 1.5
library(reshape2) # v 1.4.4
library(lavaan) # v 0.6-15
library(semPlot)
library(jmv)
library(psych)
```
 
 # Setup and initial testing
## Data cleaning
```{r setup, include=FALSE}
workdir <- # work directory
structural_brain <- # list of subjects included in the structural sample
functional_brain <- # list of subjects included in the functional sample

exposome_crosssectional <- # all timepoint 1 subject exposome data
exposome_crosssectional.filt <- exposome_crosssectional %>% filter(ID %in% structural_brain$ID) 
exposome_longitudinal <- # all timepoint subject exposome data
exposome_longitudinal.filt <- exposome_longitudinal %>% filter(ID %in% functional_brain$ID)

crime_vars <- c('Murder','Rape','Assau','Robb','Burg','Lar')

structural_crime <- exposome_crosssectional.filt[, crime_vars]
functional_crime <- exposome_longitudinal.filt[, crime_vars]

sapply(structural_crime, class) # check for numeric
sapply(functional_crime, class) # check for numeric

```
## Test for data skewness
### Structural sample
```{r setup, include=FALSE}
descriptives(data = structural_crime,
             sd =TRUE, #Lists standard deviations
             variance =TRUE, #Lists variances 
             ci =TRUE, #Lists confidence intervals (default: 95%)
             boxLabelOutliers =TRUE, #Lists rows with outliers
             hist =TRUE) #Creates histograms for variables
```

### Functional sample
```{r setup, include=FALSE}
descriptives(data = functional_crime,
             sd =TRUE, #Lists standard deviations
             variance =TRUE, #Lists variances 
             ci =TRUE, #Lists confidence intervals (default: 95%)
             boxLabelOutliers =TRUE, #Lists rows with outliers
             hist =TRUE) #Creates histograms for variables
```

#

# Model formulas
## Parallel one-factor
```{r setup, include=FALSE}
parallel_onefactor <- '
#All loads are fixed to 1
Crime=~1*Murder+1*Rape+1*Assau+1*Robb+1*Burg+1*Lar

#Fix error (residual) variances (labeled ervar) are constrained to be equal across indicators
Murder~~ervar*Murder
Rape~~ervar*Rape
Assau~~ervar*Assau
Robb~~ervar*Robb
Burg~~ervar*Burg
Lar~~ervar*Lar
'
```
## Congeneric one-factor
```{r setup, include=FALSE}
congeneric_onefactor <- '
#All loadings are uniquely estimated; First loading set to 1 by default and must be freed
Crime=~NA*Murder+Rape+Assau+Robb+Burg+Lar

#Fix latent variable variance to 1
Crime~~1*Crime
'
```
## Congeneric two-factor
```{r setup, include=FALSE}
congeneric_twofactor <- '
#All loadings are uniquely estimated; First loading set to 1 by default and must be freed
ViolentCrime=~NA*Murder+Rape+Assau
NonViolentCrime=~NA*Robb+Burg+Lar

#Fix latent variable variances to 1
ViolentCrime~~1*ViolentCrime
NonViolentCrime~~1*NonViolentCrime

#Estimate latent variable covariance
ViolentCrime~~NonViolentCrime
'
```
#

# Exposome-structural measure sample (N=170)
## Model fitting
### Parallel one-factor
```{r setup, include=FALSE}
structural_parallel_onefactor <- sem(model = parallel_onefactor,
                                     data = structural_crime,
                                     missing = 'fiml',
                                     estimator = 'MLR')
semPaths(structural_parallel_onefactor, what = "std")
summary(structural_parallel_onefactor, 
        fit.measures=TRUE,
        standardized=TRUE,
        rsquare=TRUE,
        ci=TRUE)
```
### Congeneric one-factor
```{r setup, include=FALSE}
structural_congeneric_onefactor <- sem(model = congeneric_onefactor,
                                       data = structural_crime,
                                       missing = 'fiml',
                                       estimator = 'MLR')
semPaths(structural_congeneric_onefactor, what = "std")
summary(structural_congeneric_onefactor, 
        fit.measures=TRUE,
        standardized=TRUE,
        rsquare=TRUE,
        ci=TRUE)
```
### Congeneric two-factor
```{r setup, include=FALSE}
structural_congeneric_twofactor <- sem(model = congeneric_twofactor,
                                       data = structural_crime,
                                       missing = 'fiml',
                                       estimator = 'MLR')
semPaths(structural_congeneric_twofactor, what = "std")
summary(structural_congeneric_twofactor, 
        fit.measures=TRUE,
        standardized=TRUE,
        rsquare=TRUE,
        ci=TRUE)
```

## Model comparisons using likelihood ratio tests
### Parallel one-factor & congeneric one-factor models
```{r setup, include=FALSE}
anova(structural_parallel_onefactor,
      structural_congeneric_onefactor)
```
### Congeneric one-factor & two-factor models
```{r setup, include=FALSE}
anova(structural_congeneric_onefactor,
      structural_congeneric_twofactor)
```
#

# Exposome-functional measure sample (N=130)
## Model fitting
### Parallel one-factor
```{r setup, include=FALSE}
functional_parallel_onefactor <- sem(model = parallel_onefactor,
                                     data = functional_crime,
                                     missing = 'fiml',
                                     estimator = 'MLR')
semPaths(functional_parallel_onefactor, what = "std")
summary(functional_parallel_onefactor, 
        fit.measures=TRUE,
        standardized=TRUE,
        rsquare=TRUE,
        ci=TRUE)
```
### Congeneric one-factor
```{r setup, include=FALSE}
functional_congeneric_onefactor <- sem(model = congeneric_onefactor,
                                       data = functional_crime,
                                       missing = 'fiml',
                                       estimator = 'MLR')
semPaths(functional_congeneric_onefactor, what = "std")
summary(functional_congeneric_onefactor, 
        fit.measures=TRUE,
        standardized=TRUE,
        rsquare=TRUE,
        ci=TRUE)
```
### Congeneric two-factor
```{r setup, include=FALSE}
functional_congeneric_twofactor <- sem(model = congeneric_twofactor,
                                       data = functional_crime,
                                       missing = 'fiml',
                                       estimator = 'MLR')
semPaths(functional_congeneric_twofactor, what = "std")
summary(functional_congeneric_twofactor, 
        fit.measures=TRUE,
        standardized=TRUE,
        rsquare=TRUE,
        ci=TRUE)
```

## Model comparisons using likelihood ratio tests
### Parallel one-factor & congeneric one-factor models
```{r setup, include=FALSE}
anova(functional_parallel_onefactor,
      functional_congeneric_onefactor)
```
### Congeneric one-factor & two-factor models
```{r setup, include=FALSE}
anova(functional_congeneric_onefactor,
      functional_congeneric_twofactor)
```
#


